\documentclass[hidelinks__VERSION__]{adamyi-cv}
\DeclareSymbolFont{extraup}{U}{zavm}{m}{n}
\DeclareMathSymbol{\varheart}{\mathalpha}{extraup}{86}
\begin{document}

\revision{__REVISION__}
\footertext{This version was compiled on \today\ at \DTMcurrenttime. Source code available at \href{https://github.com/hackroid/cv-new}{https://github.com/hackroid/cv-new} under MIT license.}

\header{Bohong}{Zhao}{Undergraduate | Southern University of Science and Technology}

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
(+86)17620412037
WeChat: w1231824
QQ: 1290756262
~
\href{mailto:ooozbh@gmail.com}{ooozbh@gmail.com}
\href{https://hackroid.com}{https://hackroid.com}
\href{https://github.com/hackroid}{GitHub: hackroid}
~
\href{https://www.linkedin.com/in/%E5%8D%9A%E5%BC%98-%E8%B5%B5-b7ab09136/}{LinkedIn: Bohong-Zhao}
\href{https://www.facebook.com/Hackro1d}{Facebook: Hackroid}
\section{languages}
Chinese \textbf{Native}
English \textbf{Fluency}
Japanese \textbf{Beginner}
\section{programming}
~
\textbf{Competent}
{\color{red} $\varheart$} Python
Java, C++
~
\textbf{Novice}
CSS3 \& HTML5
Kotlin, Dart
SQL, PHP, JavaSciprt
Bash/Shell, Spim
MATLAB, \LaTeX
\section{IDE\&editor}
{\color{red} $\varheart$} PyCharm
PHPStorm
~
{\color{red} $\varheart$} VSCode
Vim
Sublime
\versionsection
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------

\entry
{\href{https://www.ubc.ca/}{The University of British Columbia}, Vancouver BC Canada}
{Jul. 2018 -- Aug. 2018}
{\emph{Summer Program}\\
Studied computer science courses (algorithm \& webapp).
}

%------------------------------------------------

\entry
{\href{https://www.sustech.edu.cn/}{Southern University of Science and Technology(SUSTech)}, Shenzhen China}
{Sep. 2016 -- Jul. 2020}
{\emph{\textbf{B.S.} in Computer Science and Engineering}\\
Relavent courses: Data Structures and Algorithms Analysis, Discrete Mathematics, Digital Logic, Computer System Design and Application, Computer Organization Principle, Database Principle, Probability and Statistics, Artificial Intelligence, Computer Networks, Embedded System and Microcomputer Principle, Object-oriented Analysis and Design, Software Engineering (currently taking), C/C++ Programming Design
}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}

%------------------------------------------------

\entry
{\href{http://www.doodod.com/}{DOODO (Beijing) Ltd}}
{Aug. 2017}
{\emph{Part Time Assistant}
\begin{itemize}
\item Worked in DOODO (Beijing) Ltd and helped to create classification of user potrait.
\end{itemize}}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{awards}

\begin{entrylist}

%------------------------------------------------

\entry
{Best Student Assistant}
{Jun. 2017 -- Jun. 2018}
{\emph{\textbf{Southern University of Science and Technology}}\\
Awarded to the outstanding student assistants for helping tutor with college affairs and helping new student get into campus life.
}

%------------------------------------------------

\entry
{Undergraduate Scholarship}
{Sep. 2016}
{\emph{\textbf{Southern University of Science and Technology}}\\
Awarded to the top students at the beginning of the undergraduate.
}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%   RESEARCH SECTION
%----------------------------------------------------------------------------------------

\section{research}

\begin{entrylist}

%------------------------------------------------

\entry
{\href{https://github.com/hackroid/pMOEA-D}{Parallel Implementation of MOEA/D and its Application to Feature Selection}}
{Sep. 2018 -- present}
{\emph{In progress}
\begin{itemize}
    \item lang: Python
\end{itemize}
Team researching project under prof. \href{http://cse.sustech.edu.cn/en/people/view/people_id/55/sort_id/9/pid/}{Prof. Hisao Ishibuchi's} instruction. Evolutionary algorithm has progressive effect recent years when working on feature selection which is the most important part of machine learning and data mining. This project aims to create parallel environment for MOEA/D algorithm, using island model and find out an effective ways which partial data would used for communication. We use feature selection to verify our proposal in the whole process.
}

%------------------------------------------------

\end{entrylist}

\pagebreak

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\section{projects}

\begin{entrylist}

%------------------------------------------------

\entry
{Snappat -- A new way social network based on puzzles}
{Feb. 2019 -- present}
{\emph{In progress}
\begin{itemize}
    \item lang: Java
    \item framework: Android Original
\end{itemize}
It's an on going course project (software engineering) I and my teammates are focusing on which aims to develop a social networking app covering several features like machine learning and puzzle solving.
}

%------------------------------------------------

\entry
{\href{https://github.com/hackroid/MqttSensorDemo}{Sensor Data Real Time Transmission Application}}
{Sep. 2018 -- Jan. 2019}
{\emph{Finished}
\begin{itemize}
    \item lang: Java
    \item framework: Android Original
    \item in charge for: whole android app developemnt and server maintenance
\end{itemize}
Building an Android app to send sensor's data between multi devices using MQTT protocol. MQTT is a lightweight messaging protocol for small sensors and mobile devices and have an easy implementation and latency optimization. It's an course team project of computer network engineering and we learned the communication principle of MQTT.
}

%------------------------------------------------

\entry
{\href{https://github.com/zhaoweizhong/Faculty-Reservation}{Faculty Reservation System}}
{Sep. 2018 -- Jan. 2019}
{\emph{Finished}
\begin{itemize}
    \item lang: PHP
    \item framework: Laravel
    \item in charge for: backend PHP spider for grabbing data from researchgate
\end{itemize}
Co-developing a system to help SUSTech students and faculty schedule their appointments in a team of 5. We covered several important features in this system, such as user registration, user information, appointment scheduling, research's recent working direction and else. It's an course project of object oriented design.
}


%------------------------------------------------

\entry
{Earthquake Visualization Software}
{Feb. 2017 -- Jun. 2017}
{\emph{Finished}
\begin{itemize}
    \item lang: Java
    \item platform: JavaFX
    \item in charge for: backend Java spider for grabbing seismal data from web.
\end{itemize}
Developed a software using Java GUI and performed visualized seismal statistical data on map and also in charts. Special html content determination and slicing skills were used, and I also learned network request and response handling using Java. It's an course project of Java Programming 2 in a 3 people team.
}

%------------------------------------------------

\entry
{Flight Reservation System}
{Sep. 2016 -- Jan. 2017}
{\emph{Finished}
\begin{itemize}
    \item lang: Java, HTML\&CSS, SQL
    \item framework: JSP
    \item in charge for: Full-stack development
\end{itemize}
Led a team of 3 to develop a system and sent it online including functions like user registration, flight querying, flight reservation, flight management. I learned java bean and DOM also include OOD a little bit for the first time on my own. It's an course project of Java Programming 1.
}

%------------------------------------------------

\end{entrylist}

\end{document}
